### 2010-12-13 docs/tex/review.tex
Some changes in review

\section{Introduction}
The intention of this chapter is to discuss the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems. In addition to the model presented in chapter \ref{chapter:model}, this thesis put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process of mimicry to solve a problem in computer science.

>>>>

\section{Introduction}
This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems. In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process of mimicry to solve a problem in computer science.
